---
title: "Candy Dataset Analysis"
output: html_notebook
---

############### 1.4 Task 4 - Halloween Candy Data

##### 1.4.2 Analysis questions


## Loading packages
```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(tidyr)
library(here)
```


## Loading in csv file of cleaned data.

```{r}
candy_dataset <- read_csv(here("clean_data/candy_data_clean.csv"))
```

## 1. What is the total number of candy ratings given across the three years. (Number of candy ratings, not the number of raters. Don't count missing values)
```{r}
candy_dataset %>%
  filter(!is.na(rating)) %>%
  count(rating_id)
  
```

The total number of ratings is 595,654.


## 2. What was the average age of people who are going out trick or treating?
```{r}
candy_dataset %>%
  filter(going_trick_or_treating == "Yes") %>%
  mean(age)
```

## 3. What was the average age of people who are not going trick or treating?
```{r}
candy_dataset2 <- candy_dataset %>% 
  transform(candy_dataset, age = as.numeric(as.factor(age))) %>% 
  mutate(age = coalesce(age, 0))

candy_dataset2 %>%
  filter(going_trick_or_treating == "No") %>%
  mean("age")



```


## 4. How many people rated Starburst as despair?
```{r}
candy_dataset %>%
  filter(candy == "Starburst", rating == "DESPAIR") %>%
  count()

```

Starburst was rated DESPAIR by 1990 people.


.
## 5. What was the most popular candy bar by this rating system for each gender in the dataset ?


## 6. What was the most popular candy bar in each year?
```{r}
candy_dataset %>%
  filter(year == "2015", rating == "JOY") %>%
  group_by(candy) %>%
  count(rating)


```

